EBASE manuscript

### 2023-01-17 manu-draft.qmd
change delta to partial

$$
\frac{\delta{C_d}}{\delta{t}} = [\,aPAR^p]\, - [\,r\Theta^{T - \bar{T}}]\, - \left[-K\cdot1.0241^{T-\bar{T}}\left(C_{sat} - C_d \right )\right]
$$ {#eq-base}

where the terms in the square brackets are production (P), respiration (R), and gas exchange (D), respectively, modeled as a function of the change in dissolved oxygen ($\delta{C_d}$) per unit time ($\delta{t}$) of the input data.  Five unknown parameters are estimated from the data: $a$, $p$, $r$, $\Theta$, and $K$.  The required inputs are the time series of surface irradiance ($PAR$, $\mu$mol/m$^2$/s), water temperature ($T$, C), barometric pressure (atm), diel oxygen ($C_d$, mmol/m$^2$), and oxygen saturation ($C_{sat}$, mmol/m$^3$). Dissolved oxygen at saturation $C_{sat}$ is calculated from the input data as a function of water temperature, salinity, and barometric pressure.  Several changes, outlined and justified below, were made to @eq-base for EBASE.

@@

$$
\frac{\delta{C_d}}{\delta{t}} = [\,aPAR^p]\, - [\,r\Theta^{T - \bar{T}}]\, - \frac{1}{H}\left[-bU_{10}^2\left(\frac{s_c}{600} \right)^{-0.5} \left(C_{Sat} - C_d \right )\right]
$$ {#eq-basewan}

@@

$$
\frac{\delta{C_d}}{\delta{t}} = [\,aPAR]\, - [\,r]\, - \frac{1}{H}\left[-bU_{10}^2\left(\frac{s_c}{600} \right)^{-0.5} \left(C_{Sat} - C_d \right )\right]
$$ {#eq-ebase}

As for BASE, the metabolic estimates in EBASE are defined by the change in dissolved oxygen over the time step, $\delta{C_d}/\delta{t}$, where gross production is provided by $aPAR$, respiration is provided by $r$, and gas exchange is provided by the remainder [as in @Wanninkhof14].  Units for each of the metabolic estimates are $\runi$.

>>>>

$$
\frac{\partial{C_d}}{\partial{t}} = [\,aPAR^p]\, - [\,r\Theta^{T - \bar{T}}]\, - \left[-K\cdot1.0241^{T-\bar{T}}\left(C_{sat} - C_d \right )\right]
$$ {#eq-base}

where the terms in the square brackets are production (P), respiration (R), and gas exchange (D), respectively, modeled as a function of the change in dissolved oxygen ($\partial{C_d}$) per unit time ($\partial{t}$) of the input data.  Five unknown parameters are estimated from the data: $a$, $p$, $r$, $\Theta$, and $K$.  The required inputs are the time series of surface irradiance ($PAR$, $\mu$mol/m$^2$/s), water temperature ($T$, C), barometric pressure (atm), diel oxygen ($C_d$, mmol/m$^2$), and oxygen saturation ($C_{sat}$, mmol/m$^3$). Dissolved oxygen at saturation $C_{sat}$ is calculated from the input data as a function of water temperature, salinity, and barometric pressure.  Several changes, outlined and justified below, were made to @eq-base for EBASE.

@@

$$
\frac{\partial{C_d}}{\partial{t}} = [\,aPAR^p]\, - [\,r\Theta^{T - \bar{T}}]\, - \frac{1}{H}\left[-bU_{10}^2\left(\frac{s_c}{600} \right)^{-0.5} \left(C_{Sat} - C_d \right )\right]
$$ {#eq-basewan}

@@

$$
\frac{\partial{C_d}}{\partial{t}} = [\,aPAR]\, - [\,r]\, - \frac{1}{H}\left[-bU_{10}^2\left(\frac{s_c}{600} \right)^{-0.5} \left(C_{Sat} - C_d \right )\right]
$$ {#eq-ebase}

As for BASE, the metabolic estimates in EBASE are defined by the change in dissolved oxygen over the time step, $\partial{C_d}/\partial{t}$, where gross production is provided by $aPAR$, respiration is provided by $r$, and gas exchange is provided by the remainder [as in @Wanninkhof14].  Units for each of the metabolic estimates are $\runi$.
